Legacy Data Confounds Genomics Studies

### 2018-10-30 legacy.tex
some suggestions

\section{Discussion}
Two of these studies used HapMap as a reference panel, rather than 1000 Genomes \citep{Kraja2011, Ebejer2013}. 
The HapMap project and 1000 Genomes project shared some cell lines, however used different sequencing platforms to produce the data \sgcomment{comma splice}.
It is possible that that a cell line artifact may have produced the same suspicious SNPs in the two sequencing projects.

@@

\begin{figure}[h]
\includegraphics[width=\hsize,keepaspectratio]{./Figures/PC1_Correlation.jpg}
\caption{Regressions against the average quality per mapped bases $Q$ per individual is the best correlate with prevalence of the  *AC${\rightarrow}$*CC mutational signature in 1kGP, with individuals with low-quality data showing elevated rates of the signature.  }
\label{PC1_Correlation}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=\hsize,keepaspectratio]{./Figures/Hap_GnomAD.jpg}
\caption{Frequencies of $Q$-associated SNPs shared between 1000G and either HapMap or GnomAD. The blue and green dots in the HapMap plot are the variants reported in \citep{Mandage2017} and \citep{Kraja2011} respectively. There are 70 such SNPs in HapMap and 186 in the GnomAD.}
\label{HapMap_GnomAD}
\end{figure}

>>>>

\section{Discussion}
Two of these studies used HapMap as a reference panel, rather than 1000 Genomes \citep{Kraja2011, Ebejer2013}. 
The HapMap project and 1000 Genomes project shared some cell lines but used different sequencing platforms to produce the data.
It is possible that that a cell line artifact may have produced the same suspicious SNPs in the two sequencing projects.

@@

\begin{figure}[h]
\includegraphics[width=\hsize,keepaspectratio]{./Figures/PC1_Correlation.jpg}
\caption{\sgcomment{not regressions}Regressions against the average quality per mapped bases $Q$ per individual is the best correlate with prevalence of the  *AC${\rightarrow}$*CC mutational signature in 1kGP, with individuals with low-quality data showing elevated rates of the signature.  }
\label{PC1_Correlation}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=\hsize,keepaspectratio]{./Figures/Hap_GnomAD.jpg}
\caption{Frequencies of $Q$-associated variants polymorphic in both 1000G and either HapMap or GnomAD. \sgcomment{Change title, check targeted  sequencing region. Specify proportion of SNPs not included} The blue and green dots in the HapMap plot are the variants reported in \citep{Mandage2017} and \citep{Kraja2011} respectively. There are 70 such SNPs in HapMap and 186 in the GnomAD.}
\label{HapMap_GnomAD}
\end{figure}
